%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% Can use fonts roboto, calibri, or times new roman
\documentclass[calibri]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% For hyperliniks
\usepackage{hyperref}

% Set applicant's personal data for header
\name{ALEC CARLYLE}
\email{alec.c.carlyle@gmail.com}
\location{Fredericksburg, VA}
\phone{(540) 699-0821}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Experience}
		\begin{cvsubsection}{\textit{Software Engineer}, NSWC Dahlgren -- Dahlgren, VA}{June 2017 - Present}
			\begin{itemize}
				\item Lead development for a \textbf{Python Tkinter MySQL} application allowing analysts to build/autonomously execute regression tests between various elements in a complex naval combat system by interfacing live virtualized radar software with simulated weapon system components utilizing autogenerated \textbf{Lua} scripts and \textbf{RTI Connext DDS}. 
				\item Scrum master for a team of 6 radar integration analysts.
				\item Created 'plug-and-play' plugin architecture in \textbf{C} supporting custom network message filtering for a multithreaded 4 channel 10GbE network TAP application.  
				\item Experienced troubleshooting software issues by deep diving through millions of lines of polyglot radar software and identifying trouble areas and proposing solutions.  
				\item Rebuilt and optimized a multithreaded client/server regression test application utilizing \textbf{C++}, \textbf{QThreads}, and \textbf{Qt Signals and Slots}.   
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{\textit{DON Pathways Intern}, NSWC Dahlgren -- Dahlgren, VA}{Summer 2015, Summer 2016}	
			\begin{itemize}
				\item Summer 2016 -- Designed a \textbf{Qt Creator GUI} to parse and export hundreds of gigabytes of radar data to an external analysis tool.  
				\item Summer 2015 - Developed core radar analysis libraries in \textbf{C++} for a custom tool suite to support the integration effort for an in-development naval radar (SPY6).  
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{\textit{capitaliSim}}{\href{https://github.com/acarlyle/shopvr}{\underline{\textcolor{ColorDarkBlue}{[https://github.com/acarlyle/shopvr]}}}}
			\begin{itemize}
				\item A shopkeep role-playing simulation game in virtual reality (VR).
				\item Built in \textbf{C\#} with the \textbf{Unity} game engine for the \textbf{SteamVR} platform.  
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{\textit{dotpull}}{\href{https://github.com/acarlyle/dotpull}{\underline{\textcolor{ColorDarkBlue}{[https://github.com/acarlyle/dotpul]l}}}}	
			\begin{itemize}
				\item A Sokoban-like puzzle game initially built for the Finally Finish Something 2018 game jam.  
				\item Built with the \textbf{GameMaker Studio} engine using the \textbf{GameMaker Language (GML)} programming language.  
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{\textit{Application Station}}{\href{https://github.com/acarlyle/InformationStation}{\underline{\textcolor{ColorDarkBlue}{[https://github.com/acarlyle/InformationStation]}}}}		
			\begin{itemize}
				\item A multi-page \textbf{Python Flask} Create, Read, Update, Destroy (CRUD) \textbf{MySQL} web application for managing and registering for the student-teacher program at the University of Mary Washington.   
				\item Practiced Agile and Scrum with 3 other developers throughout the requirements gathering/analysis/specification and developmental design/integration/testing software engineering processes. 
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Education}
		\begin{cvsubsection}{University of Mary Washington -- Fredericksburg, VA}{Fall 2015 -- Spring 2017}
			\begin{itemize}
				\item Bachelor of Science in Computer Science, May 2017. GPA: 3.82/4.00
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{Germanna Community College -- Fredericksburg, VA}{Fall 2012 -- Spring 2015}
			\begin{itemize}
				\item Associate of Arts in General Studies, Spring 2015. GPA: 3.95/4.00
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Languages: Python, C++, MySQL, C, C\#, GML, Bash scripting, HTML/CSS, Lua, JavaScript, Perl, Java, R 
				\item Tools: Git, Linux, Jira
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}
